---
title: "Class 11: Structural Bioinformatics Part 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Revisit PDB

#Q1
 Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” > “by Experimental Method and Molecular Type”.  Move this CSV file into your RStudio project and determine the percentage of structures solved by X-Ray and Electron Microscopy.  Also can you determine what proportion of structures are protein?

 
```{r}
db <- read.csv("Data Export Summary.csv",row.names = 1)

#Number of Total Entries
sum(db$Total)

#Percent of structures solved by X-ray and EM
rowSums(db[,1:4])/sum(db$Total)*100

#Proportion of Structure that are Protein and Nucleic Acid, Respectively
sum(db$Proteins)/sum(db$Total)*100
sum(db$Nucleic.Acids)/sum(db$Total)*100





```

#Section 3.3

```{r}
library(bio3d)
pdb <- read.pdb("1hsg")
print(pdb)

```

```{r}
aa321(pdb$seqres)
str(pdb$atom)
```

Section 4

```{r}
ca.inds <-atom.select(pdb, "calpha")
ca.inds

```

##Atom Selection Examples

```{r}
atom.select(pdb,resno=10)
```


1hsg_protein <- 
```{r}

hsgprotein <- atom.select(pdb, "protein", value=TRUE)
hsgprotein


write.pdb(hsgprotein, file="1hsg_proteinpdb")

ligand <- atom.select(pdb, "ligand", value=TRUE)
write.pdb(ligand, file="1hsg_ligand")

```

```{r}
library("bio3d.view")
view(pdb, "overview", col="sse")
```




#Section 6.2 Aligning multiple Structures
```{r}

ids <-c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")

files <-get.pdb(ids, split =TRUE)


# Extract and align the chains we are interested in
pdbs <-pdbaln(files, fit =TRUE)


pdbs
```


```{r}
# Calculate sequence identity
seqidentity(pdbs) 

# Calculate RMSDs
rmsd(pdbs)
```

```{r}
# Calculate RMSD
rd <-rmsd(pdbs)
# Clustering
hc <-hclust(as.dist(rd))
grps <-cutree(hc, k=3)
# Plot results as dendrogram
hclustplot(hc, k=3)
```

```{r}
# Perform PCA 
pc.xray <-pca(pdbs)

# Plot our results summary (PCA score plot and scree-plot)
plot(pc.xray)


# Visualize first principal component 
pc1 <- mktrj(pc.xray, pc=1, file="pc_1.pdb")
view(pc1)

```





```{r}
aa <- get.seq("1ake_A")

#Blast or hmmer search
b <- blast.pdb(aa)

# Plot a summary of search results
hits <-plot(b)
```





```{r}
head(hits$pdb.id)
```








